The investment strategy based on behavior of artificial earthworm for use in algotrading

### 2014-05-12 Article/Article20140406Granada/LatexArt/article_main.tex
Conclusion

Presented in the paper the concept of an innovative investment strategy gave satisfactory results for a certain pair as the result of periods of machine learning. For example, in the studied data for two key market currency pairs sampled every hour, the best value is 80 hours of teaching and 15 hours of testing. One can assume that this relationship may change in a different environment (for other markets, for other periods) by becoming a sort of next parameter that optimal values should be sought. It should be emphasized that the study was conducted on data not used in the learning phase and for the basic principle of machine learning achieved results that would have satisfied many a practice. It should also be noted that outside research conducted in environment completely specified (for constant unchanging data stored in MATLAB) was also performed simulations in terms of actual brokerage platform. The results obtained in both environments are similar in the sense of direction changes and logic behavior caused by the user received by the algorithm implemented in the MATLAB and MetaTrader. Differences were explained in this work.
The direction of further research will test the hypothesis that the variability periods to test the learner can improve the quality of prediction. This hypothesis seems to be interesting against the background of previous experiences and results, eg for different studied strategies, including \cite{Wilinski2014}\cite{Wilinski}\cite{sinclare}\cite{krutsinger} obtained surprisingly different optimal length of periods of learning and testing.

>>>>

The concept of an innovative investment strategy gave satisfactory results for a certain pair as the result of periods of machine learning. E.g. in the studied data for two key market currency pairs sampled every hour, the best value is 80 hours of teaching and 15 hours of testing. One can assume that this relationship may change in a different environment (for other markets, for other periods) by becoming a sort of next parameter that optimal values should be sought. It should be emphasized that the study was conducted on data not used in the learning phase and for the basic principle of machine learning achieved results that would have satisfied many a practice. It should also be noted that outside research conducted in environment completely specified (for constant unchanging data stored in MATLAB) was also performed simulations in terms of actual brokerage platform. The results obtained in both environments are similar in the sense of direction changes and logic behavior caused by the user received by the algorithm implemented in the MATLAB and MetaTrader. Differences were explained in this work.
The direction of further research will test the hypothesis that the variability periods to test the learner can improve the quality of prediction. This hypothesis seems to be interesting against the background of previous experiences and results, eg for different studied strategies, including \cite{Wilinski2014}\cite{Wilinski}\cite{sinclare}\cite{krutsinger} obtained surprisingly different optimal length of periods of learning and testing.
